Digging Deeper Into the State of the Practice for Domain Specific Research Software

### 2022-02-17 StateOfPractice/Papers/ICCS-2022-SOP_MethodologyPlusExamples/DigDeep.tex
Reformatted tools table, added an additional row in Table 3

\begin{table}[!h]
\begin{center}
\begin{tabular}{ p{3cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm} }
\toprule
~ \ & \cite{USGS2019} & \cite{TobiasEtAl2018} & \cite{BrettEtAl2021} & \cite{WilsonEtAl2016} & \cite{SmithAndRoscoe2018} & \cite{HerouxEtAl2008} & \cite{ThielEtAl2020} & \cite{vanGompelEtAl2016} & \cite{OrvizEtAl2017}\\
\midrule
LICENSE & \checkmark &  & \checkmark & \checkmark & \checkmark & & \checkmark & \checkmark & \checkmark\\
README &  &  &  &  & & & & \\
CONTRIBUTING &  &  &  &  & & & & & \\
CITATION &  &  &  &  & & & & & \\
CHANGELOG &  &  &  &  & & & & & \\
INSTALL &  &  &  &  & & & & & \\
Uninstall &  &  &  &  & & & & & \\
Contributor Guide &  &  &  &  & & & & & \\
Getting started &  &  &  &  & & & & & \\
Tutorials &  &  &  &  & & & & & \\
FAQ &  &  &  &  & & & & & \\
Dependency List &  &  &  & & & & & & \\
Issue Track &  &  &  &  & & & & & \\
Version Control &  &  &  &  & & & & &\\ 
Requirements &  &  &  &  & & & & & \\
Design &  &  &  &  & & & & & \\
API Doc. &  &  &  &  & & & & & \\
Build Scripts &  &  &  &  & & & & & \\
Unit Tests &  &  &  &  & & & & & \\
Test Plan &  &  &  &  & & & & & \\
Integ. Tests &  &  &  &  & & & & &  \\
System Tests &  &  &  &  & & & & & \\
Acceptance Tests &  &  &  &  & & & & &  \\
Regression Tests &  &  &  &  & & & & & \\
Code Style Guide &  &  &  &  & & & & & \\
Release Info. &  &  &  &  & & & & & \\
Product Roadmap &  &  &  &  & & & & & \\
\midrule
\end{tabular}
\caption{Commonly Recommended Artifacts in Software Development Guidelines} \label{Tbl_Guidelines}
\end{center}
\end{table}

@@

\begin{table}
	\begin{center}
	\begin{tabular}{ p{5.3 cm} p{4.9 cm} p{5 cm}}
	\toprule
	\textbf{Development Tools} & \textbf{Dependencies} & \textbf{Project
	Management Tools} \\
	\midrule
	Continuous Integration & Build Automation Tools & Collaboration Tools\\
	Code Editors & Technical Libraries & Email\\
	Development Environments & Domain Specific Libraries & Change Tracking Tools\\
	Runtime Environments &  & Version Control Tools\\
	Compilers &  & Document Generation Tools\\
	Unit Testing Tools &  & \\
	Correctness Verification Tools &  & \\
	\bottomrule
	\end{tabular}
	\caption{Observed development tools, dependencies and project management
	tools} \label{tbl_tools}
	\end{center}
\end{table}

>>>>

\begin{table}[!h]
\begin{center}
\begin{tabular}{ p{3cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm}p{1cm} }
\toprule
~ \ & \cite{USGS2019} & \cite{TobiasEtAl2018} & \cite{BrettEtAl2021} & \cite{WilsonEtAl2016} & \cite{SmithAndRoscoe2018} & \cite{HerouxEtAl2008} & \cite{ThielEtAl2020} & \cite{vanGompelEtAl2016} & \cite{OrvizEtAl2017}\\
\midrule
LICENSE & \checkmark &  & \checkmark & \checkmark & \checkmark & & \checkmark & \checkmark & \checkmark\\
README &  &  &  &  & & & & \\
CONTRIBUTING &  &  &  &  & & & & & \\
CITATION &  &  &  &  & & & & & \\
CHANGELOG &  &  &  &  & & & & & \\
INSTALL &  &  &  &  & & & & & \\
Uninstall &  &  &  &  & & & & & \\
Contributor Guide &  &  &  &  & & & & & \\
Getting started &  &  &  &  & & & & & \\
User manual &  &  &  &  & & & & & \\
Tutorials &  &  &  &  & & & & & \\
FAQ &  &  &  &  & & & & & \\
Dependency List &  &  &  & & & & & & \\
Issue Track &  &  &  &  & & & & & \\
Version Control &  &  &  &  & & & & &\\ 
Requirements &  &  &  &  & & & & & \\
Design &  &  &  &  & & & & & \\
API Doc. &  &  &  &  & & & & & \\
Build Scripts &  &  &  &  & & & & & \\
Unit Tests &  &  &  &  & & & & & \\
Test Plan &  &  &  &  & & & & & \\
Integ. Tests &  &  &  &  & & & & &  \\
System Tests &  &  &  &  & & & & & \\
Acceptance Tests &  &  &  &  & & & & &  \\
Regression Tests &  &  &  &  & & & & & \\
Code Style Guide &  &  &  &  & & & & & \\
Release Info. &  &  &  &  & & & & & \\
Product Roadmap &  &  &  &  & & & & & \\
\midrule
\end{tabular}
\caption{Commonly Recommended Artifacts in Software Development Guidelines} \label{Tbl_Guidelines}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{ p{12 cm}}
%\toprule
\textbf{Development Tools}\\
\midrule
Continuous Integration, Code Editors, Development Environments, Runtime
Environments, Compilers, Unit Testing Tools, Correctness Verification Tools\\
%\midrule
\textbf{Dependencies}\\
\midrule
Build Automation Tools, Technical Libraries, Domain Specific Libraries\\
%\midrule
\textbf{Project Management Tools}\\
\midrule
Collaboration Tools, Email, Change Tracking Tools, Version Control Tools, Document Generation Tools\\
%\bottomrule
\end{tabular}
\caption{Observed development tools, dependencies and project management tools} 
\label{tbl_tools}
\end{center}
\end{table}
